\documentclass{article}

% To improve reproducibility, don't include certain metadata generated from the
% system date and time.
% \pdfvariable suppressoptionalinfo \numexpr32+64+512\relax

% Language setting
\usepackage[english]{babel}

% Set page size and margins
\usepackage[a4paper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{geometry}

% Set title, authr and date
\title{\textbf{Migraines and Math Degrees: A Spurious Love Story}}
\author{Researchers with a Sense of Humor}
\date{May 28, 2025}


\begin{document}
\maketitle

\begin{abstract}
  In this groundbreaking investigation, we explore a striking and absolutely questionable correlation between the number of Master's degrees awarded in Mathematics and Statistics, and the frequency of Google searches for the phrase ``why do I have a migraine'' from 2012 to 2021. While the relationship is likely spurious, the implications for public health, education, and the cosmic balance of the universe are clearly profound.
\end{abstract}

\begin{section}{Introduction}
 Correlations are everywhere---sometimes meaningful, other times hilariously coincidental. Inspired by the timeless wisdom of tylervigen.com, we delved into a curious trend: as the number of Master's degrees awarded in Mathematics and Statistics increases, so too does public interest in migraines, as measured by Google search queries.
\end{section}

\begin{section}{Data and Methods}
 We utilized data featured by Tyler Vigen, drawn from publicly available sources:
 \begin{itemize}
   \item \textbf{Master's degrees awarded in Mathematics and Statistics}: National Center for Education Statistics.
   \item \textbf{Google searches for ``why do I have a migraine''}: Google Trends.
 \end{itemize}
 The analysis covered the years 2012 through 2021. Pearson's correlation coefficient was used to measure the linear relationship, yielding a stunning $r = 0.9499$ with $r^2 = 0.9023$.
\end{section}

\begin{section}{Results}
 The correlation coefficient of $r = 0.9499$ suggests an almost comically strong linear relationship. Approximately 90.2\% of the variation in migraine search frequency could be ``explained'' by math degree trends. The data paints a picture of synchronized suffering.
\end{section}

\begin{section}{Discussion}
 Several hypotheses could explain this correlation:
 \begin{itemize}
   \item Pursuing a Master's degree in Mathematics and Statistics induces migraines.
   \item Sufferers of migraines seek solace in rigorous mathematical study.
   \item This is all an elaborate prank by the universe.
 \end{itemize}
 Clearly, none of these should be taken seriously. Except maybe the last one.
\end{section}

\begin{section}{Conclusion}
 Is this correlation real? Yes. Is it meaningful? No. Should you change careers or question your reality because of it? Absolutely. But more than anything, remember: correlation is not causation—but it sure is fun.
\end{section}

\begin{section}{Acknowledgments}
 We thank Tyler Vigen for inspiring this research and providing the data. We also thank our families for their patience as we spent countless hours analyzing this utterly ridiculous correlation.
\end{section}

% Include the generated file.
\input{./generated/example.tex}


\end{document}
